Parallel Multipoint Approximation Method for Large Scale Optimization Problems \thanks{This study was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2018-01-24 2018/PAVT_Toropov/PAVT2018_MAM.tex
Final version

The Moving Least Squares Method (MLSM) was proposed in \cite{LancasterSalkauskas1981} for smoothing and interpolation of scattered data and later used in the mesh-free form of the FEM \cite{Liszka1984}. As suggested in \cite{ChoiYounYang2001}, it can be used as a technique for metamodelling and used in MDO frameworks. The MLSM is a weighted least squares method where the weights depend on the Euclidean distance from a sample point to where the surrogate model is to be evaluated. The weight value for a certain sample point decays as the distance increases. Describing the weight decay with a Gaussian function tends to be the most useful option even though many others have been evaluated in \cite{ToropovSchrammSahaiJones2005}. As demonstrated in \cite{PolynkinToropov2010}, the cross-validated MLSM can be used both for design variable screening and for surrogate modelling. In order to create an efficient MDO framework for problems with disparate discipline attributes \cite{OllarToropovJones2014} extended the optimization approach of MAM to the use of local DOEs and MLS approximations built in different subspaces of the total design variable space corresponding to the individual disciplines. The subspaces are finally combined into the total design variable space in which the resulting MDO problem is solved.

@@

\bibitem{ToropovFilatov1993}
Toropov, V., Filatov, A., Polynkin, A.:
\newblock Multiparameter structural optimization using fem and multipoint explicit approximations.
\newblock Structural Optimization \textbf{6}, 7--14 (1993)

@@

%\bibitem{Strongin2000}
%Strongin, R.G., Sergeyev, Y.D.: Global Optimization with Non-Convex Constraints. Sequential and Parallel Algorithms. Kluwer Academic Publishers, Dordrecht (2000); DOI: 10.1007/978-1-4615-4677-1
%
%\bibitem{Barkalov2002}
%Barkalov, K.A., Strongin, R.G.: A global optimization technique with an adaptive order of checking for constraints. Comput. Math. Math. Phys. 42(9), 1289--1300 (2002)
%
%\bibitem{Gergel2005}
%Gergel, V.P., Strongin, R.G.: Parallel computing for globally optimal decision making on cluster systems. Future Gener. Comput. Syst. 21(5), 673--678 (2005); DOI: 10.1016/j.future.2004.05.007
%
%\bibitem{Strongin2013}
%Sergeyev, Ya.D., Strongin, R.G., Lera, D.: Introduction to global optimization exploiting space-filling curves. Springer (2013);  DOI: 10.1007/978-1-4614-8042-6
%
%\bibitem{Barkalov2010}
%Barkalov, K., Ryabov, V., Sidorov, S.: Parallel Scalable Algorithms with Mixed Local-Global Strategy for Global Optimization Problems. In: Hsu, Ch., Malyshkin, V. (Eds.) MTPP 2010, LNCS, vol. 6083, pp. 232--240. Springer, Heidelberg (2010); DOI: 10.1007/978-3-642-14822-4$\_$26
%
%\bibitem{Barkalov2015}
%Barkalov, K., Gergel, V., Lebedev, I.: Use of Xeon Phi Coprocessor for Solving Global Optimization Problems. In: Malyshkin, V. (Ed.) PaCT 2015, LNCS, vol. 9251, pp. 307--318. Springer, Heidelberg (2015); DOI: 10.1007/978-3-319-21909-7$\_$31
%
%\bibitem{Barkalov2016}
%Barkalov, K., Gergel, V.: Parallel Global Optimization on GPU. J. Glob. Optim. 66(1), 3--20 (2016); DOI: 10.1007/s10898-016-0411-y
%
%\bibitem{Gergel2016}
%Barkalov, K., Gergel, V., Lebedev, I.: Solving Global Optimization Problems on GPU Cluster. In: Simos T.E. (Ed.) ICNAAM 2015, AIP Conference Proceedings, vol. 1738, art. no. 400006 (2016); DOI: 10.1063/1.4952194
%
%\bibitem{Gergel2015}
%Gergel, V., Sidorov, S.: A Two-Level Parallel Global Search Algorithm for Solution of Computationally Intensive Multiextremal Optimization Problems. In: Malyshkin, V. (Ed.) PaCT 2015, LNCS, vol. 9251, pp. 505--515. Springer, Heidelberg (2015); DOI: 10.1007/978-3-319-21909-7$\_$49
%

%\end{thebibliography}

>>>>

The Moving Least Squares Method (MLSM) was proposed in \cite{LancasterSalkauskas1981} for smoothing and interpolation of scattered data and later used in the mesh-free form of the finite element method (FEM) \cite{Liszka1984}. As suggested in \cite{ChoiYounYang2001}, it can be used as a technique for metamodelling and used in multidisciplinary optimization (MDO) frameworks. The MLSM is a weighted least squares method where the weights depend on the Euclidean distance from a sample point to where the surrogate model is to be evaluated. The weight value for a certain sample point decays as the distance increases. Describing the weight decay with a Gaussian function tends to be the most useful option even though many others have been evaluated in \cite{ToropovSchrammSahaiJones2005}. As demonstrated in \cite{PolynkinToropov2010}, the cross-validated MLSM can be used both for design variable screening and for surrogate modelling. In order to create an efficient MDO framework for problems with disparate discipline attributes \cite{OllarToropovJones2014} extended the optimization approach of MAM to the use of local DOEs and MLS approximations built in different subspaces of the total design variable space corresponding to the individual disciplines. The subspaces are finally combined into the total design variable space in which the resulting MDO problem is solved.

@@

\bibitem{ToropovFilatov1993}
Toropov, V., Filatov, A., Polynkin, A.:
\newblock Multiparameter structural optimization using FEM and multipoint explicit approximations.
\newblock Structural Optimization \textbf{6}, 7--14 (1993)

@@
